ResultsNPS

### 2019-12-05 R/nps_reports/results.Rmd
changes to dataset reading in R. Generalized so less code.

---
title: "ResultsNPS"
author: "Franco Peschiera"
date: "August 8, 2019"
output:
  html_document: default
  pdf_document: default
params:
  size: get_3_tasks_aggresive_perc_add
  scale: log2
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
# setwd('../')
# browser()
source('nps_reports/functions.R')
source('nps_reports/datasets.R')
default_tail <- 0.05
really_small_number <- 0.000001
size <- params$size
df <- do.call(size, args=list())
value_filt_tails <- function(value, each_tail) value %>% between(., quantile(., c(each_tail[1])), quantile(., c(1-each_tail[2])))

>>>>

---
title: "ResultsNPS"
author: "Franco Peschiera"
date: "August 8, 2019"
output:
  html_document: default
  pdf_document: default
params:
  size: get_3_tasks_aggresive_perc_add
  scale: log2
  num_tasks: 2
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
# setwd('../')
# browser()
source('nps_reports/functions.R')
source('nps_reports/datasets.R')
default_tail <- 0.05
really_small_number <- 0.000001
size <- params$size
df <- do.call(size, args=params)
value_filt_tails <- function(value, each_tail) value %>% between(., quantile(., c(each_tail[1])), quantile(., c(1-each_tail[2])))
